---
title: "Homework 1"
author: Ling Tuo
date: 09/19/2020
output: 
  github_document:
    toc: true
---

This is my solution to HW1. 

```{r, message = FALSE}
library(tidyverse)
```

## Problem 1

Create a dataframe with specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r means, collapse = TRUE}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r as_numeric, collapse = TRUE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

Logical and factor variables can be converted into numeric but character cannot.

```{r convert, collapse = TRUE}
as.numeric(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0))*pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0)))*pull(prob1_df, samp)
```


## Problem 2

Load the `penguins` dataset:

```{r}
data("penguins", package = "palmerpenguins")
```

Description of the `penguins` dataset:

* The names of the variables in the dataset are **`r names(penguins)`**.

* The values of these variables can be generally described as follows.

  + The variable **`r names(penguins[1])`** has class `r class(pull(penguins, species))` 
  and levels are `r levels(pull(penguins, species))`.
  
  + The variable **`r names(penguins[2])`** has class `r class(pull(penguins, island))` 
  and levels are `r levels(pull(penguins, island))`.
  
  + The variable **`r names(penguins[3])`** has class `r class(pull(penguins, bill_length_mm))` 
  with a range of [`r range(pull(penguins, bill_length_mm), na.rm = TRUE)`].
  
  + The variable **`r names(penguins[4])`** has class `r class(pull(penguins, bill_depth_mm))` 
  with a range of [`r range(pull(penguins, bill_depth_mm), na.rm = TRUE)`].
  
  + The variable **`r names(penguins[5])`** has class `r class(pull(penguins, flipper_length_mm))` 
  with a range of [`r range(pull(penguins, flipper_length_mm), na.rm = TRUE)`].
  
  + The variable **`r names(penguins[6])`** has class `r class(pull(penguins, body_mass_g))` 
  with a range of [`r range(pull(penguins, body_mass_g), na.rm = TRUE)`].
  
  + The variable **`r names(penguins[7])`** has class `r class(pull(penguins, sex))` 
  and levels are `r levels(pull(penguins, sex))`.
  
  + The variable **`r names(penguins[8])`** has class `r class(pull(penguins, year))` 
  with a range of [`r range(pull(penguins, year), na.rm = TRUE)`].

* The dataset has `r nrow(penguins)` rows (elements) and `r ncol(penguins)` columns (variables).

* The mean of the flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`.

Here is the scatterplot of flipper_length_mm (y) vs bill_length_mm (x):

```{r yx_scatter}
plot_df = tibble(
  x = pull(penguins, bill_length_mm),
  y = pull(penguins, flipper_length_mm)
)
species = pull(penguins, species)
ggplot(plot_df, aes(x = x, y = y, color = species)) + geom_point(na.rm = TRUE)
```

Export the scatterplot.

```{r, eval = FALSE}
ggsave("plot_hw1.pdf")
```

